
\documentclass{report}

\usepackage{html}
\usepackage{verbatim}
\usepackage{alltt}
\usepackage{makeidx}
\usepackage{scdoc}

\setcounter{tocdepth}{1}

\makeindex

\begin{document}

\title{The SC Programmer's Manual}

\author{Curtis L. Janssen \and Edward T. Seidl \and Ida M. B. Nielsen
        \and Michael E. Colvin}

\date{\today}

\maketitle

\begin{abstract}

The Scientific Computing (SC) toolkit provides C++ class libraries of use
in scientific computation.  Included are classes for managing memory,
saving and restoring the state of objects, reading objects from an input
file, parallel communication, matrix algebra, among others.

SC runs on Unix compatible workstations (Intel/Linux,
IBM RS/6000), symmetric multi-processors (Intel/Linux),
and massively parallel computers (IBM SP2, Intel Paragon).

\end{abstract}

\tableofcontents

\part{Overview}

\chapter{Introduction}

The Scientific Computing (SC) toolkit provides C++ class libraries for
scientific computation.  Included are classes for managing memory, saving
and restoring the state of objects, reading objects from an input file,
parallel communication, matrix algebra, among others.

SC runs on Unix compatible workstations (Intel/Linux,
IBM RS/6000), symmetric multi-processors (Intel/Linux),
and massively parallel computers (IBM SP2, Intel Paragon).

The SC toolkit is a work-in-progress.  Thus, this manual is incomplete.
Furthermore, some of the classes in the distribution may be on the verge of
obsolescence and others may be unfinished work that are intended to provide
new functionality in later releases.

The development of SC has been driven by the development of the Massively
Parallel Quantum Chemistry (MPQC) program.  While, currently, MPQC nad SC
are distributed together, the toolkit code is independent of the quantum
chemistry code.  The classes provided in src/lib/util do not require those
in src/lib/math or src/lib/chemistry and the src/lib/math classes do not
require src/lib/chemistry.  To compile SC on your machine refer to the
MPQC User Manual.

\chapter{The Source Distribution}

\begin{description}
\item[\filnm{bin}]  This directory mainly contains commands that
  are used to help with the compilation of SC.

\item[\filnm{include/libg++-stub}]  This provides a few include
  files taken from GNU libg++.

\item[\filnm{lib/basis}] The Gaussian basis set data files are in this
  directory.

\item[\filnm{lib/elisp}] If you are an emacs user, some useful
  modes and C++ programming style specifications can be found
  here.

\item[\filnm{lib/perl}] Perl modules that are used by the MPQC
  validation suite are found here.

\item[\filnm{lib/texinputs}] A style file for the SC documenation
  is located in this directory.
  
\item[\filnm{src/tools/mkclasses}]  This is intended to generate a
  database for dynamic class library loading, but currently isn't used.

\item[\filnm{src/lib/util/options}]
  This contains the GetLongOpt command line argument parsing facility
  written by S. Manoharan, with some modifications.

\item[\filnm{src/lib/util/ref}]
  This library provides memory management for objects.

\item[\filnm{src/lib/util/container}] This library provides container
  classes.  Some of these classes are not very efficient and it is likely
  that they will be replaced by the C++ Standard Template Library when it
  is supported fully by more compilers.

\item[\filnm{src/lib/util/misc}] This contains a variety of independent
  classes that don't belong anywhere else.  Classes to assist with
  debugging, provide information about hte execution environment, help make
  the output prettier, maintain detailed timing information, etc. are
  provided.

\item[\filnm{src/lib/util/class}] This library provides base classes for
  classes that require a common interface for obtaining meta-information
  about the class.  This meta-information includes the class name,
  meta-information about the parent class and derived classes that have
  been linked into the executable, pointers to functions that can create
  instances of the class, and so on.

\item[\filnm{src/lib/util/keyval}] This library provides classes that read
  keyword/value pairs from an input file.

\item[\filnm{src/lib/util/state}] The state library provides a base class
  for persistent objects and classes to read and write these objects to a
  stream.

\item[\filnm{src/lib/util/group}] This group library provides classes to
  communicate between nodes of a parallel machine.  Message passing,
  distributed shared memory, and multi-threaded models are supported.

\item[\filnm{src/lib/util/render}] This library provides an abstract
  interface to rendering packages.  This code is not currently used and
  will likely change quite a bit in the future.

\item[\filnm{src/lib/math/linpackd}] This library contains double precision
  C versions of some of the linpack routines.

\item[\filnm{src/lib/math/scmat}] This library defines an abstract matrix
  class and supplies concrete implementations of parallel replicated and
  distributed matrices.

\item[\filnm{src/lib/math/optimize}] The optimize library provides classes
  to perform optimizations and base classes for objects that compute a
  scalar quantity as a function of several coordinates.

\item[\filnm{src/lib/math/topology}] These utility classes will be replaced
  in a future release of SC.

\item[\filnm{src/lib/math/isosurf}] This library can be used to compute a
  triangulated approximation to an isosurface.

\item[\filnm{src/lib/math/symmetry}] The symmetry library contains classes
  useful for describing point group symmetry.

\item[\filnm{src/lib/chemistry/molecule}] This library has classes to
  describe molecules and internal molecular coordinate systems. A base
  class for classes that map the molecular coordinates to an energy is
  provided to permit the optimization of the molecular coordinates.
  The internals of many of these classes will be revised in the
  next release.

\item[\filnm{src/lib/chemistry/solvent}]  This code can be used to
  describe solvated molecules.  It is still in its infancy and
  is not yet used by any other part of SC.

\item[\filnm{src/lib/chemistry/qc/basis}] The basis library has classes
  that describe Gaussian basis sets and base classes for libraries that
  compute integrals involving these functions.

\item[\filnm{src/lib/chemistry/qc/oint3}] This library is comprised of
  machine generated code that is only used by the intv3 library.

\item[\filnm{src/lib/chemistry/qc/intv3}] The intv3 library computes
  integrals involving Gaussian basis functions.

\item[\filnm{src/lib/chemistry/qc/wfn}] The wfn library contains base
  classes for classes that, given a molecule and a basis set, compute the
  energy and other properties of the molecule.

\item[\filnm{src/lib/chemistry/qc/scf}] The scf library is used to compute
  Hartree-Fock energies and gradients.

\item[\filnm{src/lib/chemistry/qc/mbpt}] This library computes second-order
  perturbation theory energies and gradients.

\item[\filnm{src/lib/chemistry/qc/psi}] This provides an example of
  interfacing MPQC to an external quantum chemistry package.  It
  is not compiled by default.

\item[\filnm{src/lib/chemistry/qc/g92}] This is another example of
  interfacing MPQC to an external quantum chemistry package.  It
  is not compiled by default and is out-of-date.  The psi library
  provides a better example.

\item[\filnm{src/bin/mpqc}]
  The Massively Parallel Quantum Chemistry program is in this directory.

\item[\filnm{src/bin/molrender}]
  This is a (probably nonfunctional) example of the use of the render
  library.

\item[\filnm{src/bin/orbixme}]
  An example of using Corba and SC.  This hasn't been used in quite
  some time and probably won't compile.

\end{description}

\part{Utility Libraries}

\input{util/ref/doc/refdoc.tex}
\input{util/class/doc/class.tex}
\input{util/state/doc/state.tex}
\input{util/misc/doc/misc.tex}
\input{util/group/doc/group.tex}
\input{util/keyval/doc/keyvaldoc.tex}

\part{Math Libraries}

\input{math/scmat/doc/scmat.tex}
\input{math/optimize/doc/opt.tex}
\input{math/symmetry/doc/symmetry.tex}

\part{Chemistry Libraries}

\input{chemistry/molecule/doc/moldoc.tex}

\printindex

\end{document}
