
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \clsnm{SCMatrixKit} Class}
\label{SCMatrixKit}\index{SCMatrixKit}

The \clsnm{SCMatrixKit} abstract class acts as a factory for producing
matrices.  By using one of these, the program makes sure that all of the
matrices are consistent.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \clsnm{LocalSCMatrixKit} Class}
\label{LocalSCMatrixKit}\index{LocalSCMatrixKit}

The \clsnm{LocalSCMatrixKit} produces matrices that work in a
single processor environment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \clsnm{ReplSCMatrixKit} Class}
\label{ReplSCMatrixKit}\index{ReplSCMatrixKit}

The \clsnm{ReplSCMatrixKit} produces matrices that work in a
many processor environment.  A copy of the entire matrix is stored
on each node.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \clsnm{DistSCMatrixKit} Class}
\label{DistSCMatrixKit}\index{DistSCMatrixKit}

The \clsnm{DistSCMatrixKit} produces matrices that work in a many processor
environment.  The matrix is distributed across all nodes.  Some debugging
may be required with this specialization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \clsnm{SCDimension} Class}
\label{SCDimension}\index{SCDimension}

\begin{description}
  \item[\keywd{n}] This gives size of the dimension.  One of \keywd{n} or
        \keywd{blocks} is required.

  \item[\keywd{blocks}] The block information for the dimension can be
        given as a \clsnmref{SCBlockInfo} object.  One of \keywd{n} or
        \keywd{blocks} is required.

\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \clsnm{SCBlockInfo} Class}
\label{SCBlockInfo}\index{SCBlockInfo}

\begin{description}
  \item[\keywd{sizes}]  This is a vector giving the size of each
        subblock.  There is no default.

  \item[\keywd{subdims}] If this vector is given there is must be entry for
        each entry in the \keywd{sizes} vector.  Each entry is an
        \clsnmref{SCDimension} object.  The default is to not store
        subdimension information.

\end{description}
