
\section{The \clsnm{ParsedKeyVal} Input Format}
\label{ParsedKeyVal}
\label{KeyVal}
\index{ParsedKeyVal}
\index{KeyVal}

The \clsnm{KeyVal} class provides a means for users to associate keywords
with values.  \clsnm{ParsedKeyVal} is a specialization of \clsnm{KeyVal}
that permits keyword/value associations in text such as an input file or a
command line string.

The package is flexible enough to allow complex structures and arrays as
well as objects to be read from an input file.

\subsection{Assignment}

As an example of the use of \clsnmref{ParsedKeyVal}, consider the following
input:
\begin{verbatim}
x_coordinate = 1.0
y_coordinate = 2.0
x_coordinate = 3.0
\end{verbatim}
Two assignements will be made.  The keyword \verb|x_coordinate| will be
associated with the value \verb|1.0| and the keyword \verb|y_coordinate|
will be assigned to \verb|2.0|.  The third line in the above input
will have no effect since \verb|x_coordinate| was assigned previously.

\subsection{Keyword Grouping}
\label{pkvgroup}

Lets imagine that we have a program which needs to read in the
characteristics of animals.  There are lots of animals so it might be
nice to catagorize them by their family.  Here is a sample format for
such an input file:
\begin{verbatim}
reptile: (
  alligator: (
    legs = 4
    extinct = no
    )
  python: (
    legs = 0
    extinct = no
    )
  )
bird: (
  owl: (
    flys = yes
    extinct = no
    )
  )
\end{verbatim}

This sample illustrates the use of \vrbl{keyword} \verb|=| \vrbl{value}
assignments and the keyword grouping operators \verb|(| and \verb|)|.
The keywords in this example are
\begin{verbatim}
reptile:alligator:legs
reptile:alligator:extinct
reptile:alligator:legs
reptile:python:size
reptile:python:extinct
bird:owl:flys
bird:owl:extinct
\end{verbatim}

The \verb|:|'s occuring in these keywords break the keywords into
smaller logical units called keyword segments.  The sole purpose of this
is to allow persons writing input files to group the input into easy to
read sections.  In the above example there are two main sections, the
reptile section and the bird section.  The reptile section takes the
form \verb|reptile| \verb|:| \verb|(| \vrbl{keyword} \verb|=| \vrbl{value}
assignments \verb|)|.  Each of the keywords found between the
parentheses has the \verb|reptile:| prefix attached to it.  Within each
of these sections further keyword groupings can be used, as many and as
deeply nested as the user wants.

Keyword grouping is also useful when you need many different programs to
read from the same input file.  Each program can be assigned its own
unique section.

\subsection{Array Construction}
\label{pkvarray}

Input for an array is specified in the input by forming a \htmlref{keyword
group}{pkvgroup}.  The name of the group is the name of the array and the
grouped keywords are the integers $i$, such that $0 \leq i < n$, where $n$
is the number of elements in the array.  For example, an array, called
\verb|array|, of length 3 could be given as follows:
\begin{verbatim}
array: (
  0 = 5.4
  1 = 8.9
  2 = 3.7
  )
\end{verbatim}
The numbers \verb|0|, \verb|1|, and \verb|2| in this example are keyword
segments which serve as indices of \verb|array|.  However, this syntax
is somewhat awkward and array construction operators have been provided
to simplify the input for this case.  The following input is equivalent
to the above input:
\begin{verbatim}
array = [ 5.4 8.9 3.7 ]
\end{verbatim}

More complex arrays than this can be imagined.  Suppose an array of
complex numbers is needed.  For example the input
\begin{verbatim}
carray: (
  0: ( r = 1.0  i = 0.0 )
  1: ( r = 0.0  i = 1.0 )
  )
\end{verbatim}
could be written as
\begin{verbatim}
carray: [
  (r = 1.0 i = 0.0)
  (r = 0.0 i = 1.0)
  ]
\end{verbatim}
which looks a bit nicer than the example without array construction
operators.

Furthermore, the array construction operators can be nested in about
every imaginable way.  This allows multidimensional arrays of
complicated data to be represented.  Here is an example of
input for a lower triangular array:
\begin{verbatim}
ltriarray = [ [ 5.4  ]
              [ 0.0 2.8 ]
              [ 0.1 0.0 3.7 ] ]
\end{verbatim}

%It would be nice to just extend an array that is already defined.  This
%feature has not been implemented; however, user demand for it might
%result in its implementation.  The operators reserved for this purpose
%are \verb|+[| and \verb|]|.

\subsection{Table Construction}
\label{pkvtable}

Although the \htmlref{array construction operators}{pkvarray} will suit
most requirements for enumerated lists of data, in some cases the input can
still look ugly.  This can, in some cases, be fixed with the table
construction operators, \verb|{| and \verb|}|.

Suppose a few long vectors of the same length are needed and the data in
the \verb|i|th element of each array is related or somehow belong
together.  If the arrays are so long that the width of a page is
exceeded, then data that should be seen next to each other are no longer
adjacent.  The way this problem can be fixed is to arrange the data
vertically side by side rather than horizontally.  The table
construction operators allows the user to achieve this in a very simple
manner.
\begin{verbatim}
balls: (
  color    = [  red      blue     red   ]
  diameter = [   12       14       11   ]
  material = [  rubber  vinyl   plastic ]
  bounces  = [  yes      no       no    ]
  coordinate = [[ 0.0  0.0  0.0]
                [ 1.0  2.0 -1.0]
                [ 1.0 -1.0  1.0]]
  )
\end{verbatim}
can be written
\begin{verbatim}
balls: (
  { color diameter material bounces     coordinate} =
  {  red     12    rubber    yes     [ 0.0  0.0  0.0]
     blue    14    vinyl     no      [ 1.0  2.0 -1.0]
     red     11    plastic   no      [ 1.0 -1.0  1.0] }
  )
\end{verbatim}
The length and width of the table can be anything the user desires.

\subsection{Value Substitution}
\label{ParsedKeyValvalsub}

Occasionally, a user may need to repeat some value several times in an
input file.  If the value must be changed, it would be nice to only
change the value in one place.  The value substitution feature of
\clsnmref{ParsedKeyVal} always the user to do this.  Any place a value can
occur the user can place a \verb|$|.  Following this a keyword must be
given.  This keyword must have been assigned before the attempt is made
to use its value in a value substitution.

Here is an example illustrating most of the variable substition
features:
\begin{verbatim}
default:linewidth = 130
testsub: (
  ke: (
    ke_1 = 1
    ke_2 = 2
    ke_3: (
      ke_31 = 31
      ke_32 = 32
      )
    )
  kx = $ke
  r1 = 3.0
  r2 = $r1
  linewidth = $:default:linewidth
  )
\end{verbatim}
is the same as specifying
\begin{verbatim}
testsub: (
  ke: (
    ke_1 = 1
    ke_3: (
      ke_31 = 31
      ke_32 = 32
      )
    ke_2 = 2
    )
  linewidth = 130
  r2 = 3.0
  r1 = 3.0
  kx: (
    ke_1 = 1
    ke_2 = 2
    ke_3: (
      ke_31 = 31
      ke_32 = 32
      )
    )
  )
\end{verbatim}
It can be seen from this that value substitution can result in entire
keyword segment hierarchies being copied, as well as simple
substitutions.


\subsection{Expression Evaluation}

Suppose your program requires several parameters \verb|x1|, \verb|x2|,
and \verb|x3|.  Furthermore, suppose that their ratios remain fixed for
all the runs of the program that you desire.  It would be best to
specify some scale factor in the input that would be the only thing that
has to be changed from run to run.  If you don't want to or cannot
modify the program, then this can be done directly with
\clsnmref{ParsedKeyVal} as follows
\begin{verbatim}
scale = 1.234
x1 = ( $:scale *  1.2 )
x2 = ( $:scale *  9.2 )
x3 = ( $:scale * -2.0 )
\end{verbatim}
So we see that to the right of the ``\verb|=|'' the characters
``\verb|(|'' and ``\verb|)|'' are the expression construction operators.
This is in contrast to their function when they are to the left of the
``\verb|=|'', where they are the keyword grouping operators.

The expression must be binary and the data is all converted
to double.  If you use the expression construction operators to produce
data that the program expects to be integer, you will certainly get the
wrong answers (unless the desired value happens to be zero).

\subsection{Objects}
\label{pkvobject}

An instance of an object can be can be specified by surrounding it's
classname with the ``\verb|<|'' and ``\verb|>|'' operators immediately
after the keyword naming the data.

A pointer to a single object can be associated with multiple keywords by
using
\hyperref{value substitution}
         {value substitution (see Section~}
         {)}
         {ParsedKeyValvalsub}.
This is accomplished by holding references to all objects once they are
read in.

Consider a linked list class, \clsnm{A}, which reads from the keyword
\verb|next| a reference to an object of class \clsnm{A}.  Input for such an
object, read from keyword \verb|a1|, follows:
\begin{verbatim}
a1<A>: (
    next<A>: (
        next<B>: (
            bdata = 4
            next<A>:()
            )
        )
    )
a2 = $:a
\end{verbatim}

The \verb|a1| list would contain two \verb|A| objects followed by a
\verb|B| object followed by another \verb|A| object.  The \verb|a2| list
refers to exactly the same object as \verb|a1| (not a copy of
\verb|a1|).

